---
title: "Class 16S Example Data"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  Learn how to do basic analysis for a 16S microbiome dataset
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries, include=FALSE}
library(phyloseq)
library(vegan)
library(tidyverse)
library(ggplot2)
library(Biostrings)
library(ggpubr)
library(decontam)
library(metagenomeSeq)
library(indicspecies)
```

```{r cbp, include=TRUE}
# color blind pallet
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r RDS, include=TRUE}
# This is how to read in an RDS file
physeq.css <- readRDS(file = "../RDS/Bacteria_Soil_CSSnorm_102021.rds")
physeq.clean.samples <- readRDS(file = "../RDS/Bacteria_Soil_nonnorm_102021.rds")
```

```{r parsing, include=TRUE}
# Getting comfortable 
# most abundant OTUs
most.abundant <- data.frame(sort(rowSums(physeq.clean.samples@otu_table), decreasing = TRUE))
head(most.abundant)
physeq.clean.samples@refseq$BOTU_2
```

## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

